Effect of character correlation

### 2017-07-26 Analysis/EffectCorrelation.Rmd
Separated stats bit for supplementaries

## getting the aov data
aov_data <- get.aov.data(whole_data, "RF", "norm", combined = TRUE)

@@

## NTS function of scenario (random = method + taxa + character)
model <- lmer(NTS ~ scenario + (1|method/taxa/character), data = aov_data$data)
anova(model)
difflsmeans(model, test.effs = "scenario")

## Plotting the residuals
normal_test <- shapiro.test(residuals(model))
hist(residuals(model),
    main = paste("Normal (W=", round(normal_test$statistic, digit = 2) ,
        "; p=", round(normal_test$p.value, digit = 2) ,")", sep = ""))

## Residuals vs predicted plot
plot(fitted(model), residuals(model))

## The residuals seem
```

@@

The results seem to be heterodastic

>>>>

## getting the aov data
aov_data <- get.aov.data(whole_data, "RF", "best", combined = TRUE)

@@

## NTS function of scenario (random = method + taxa + character)
model <- lmer(NTS ~ scenario + (1|method/taxa/character), data = aov_data$data)
#anova(model)
#difflsmeans(model, test.effs = "scenario")
```

First let's test our model assumptions

@@

Data is heterodastic for Triples norm + RF norm
Data is homoscedastic for Triples best + RF best
Data is non-normal for Triples norm + RF norm

The test assumptions are not validated.
We can instead use a non-parametric nested anova and a Bhattacharrya Coefficient (probability of overlap)

```{r}
##
run.bhatt.coeff(data, metric = "RF", best = "norm")

```
